Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-04 manuscript.tex
5.1 updates

When looking at the significance of the different parameters in the activity correction in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the correction, and BIS SPAN, with coefficient $\beta_2$, is not useful to explain stellar activity when using the parameters derived from the Normal density fit. However all the other parameters in the Normal and SN cases are useful to model stellar activity. By analyzing the values of $R^2$, we see that the correction is more efficient at explaining stellar activity when considering SN mean RV as the RV estimate. This is expected from the results above since for the three different RV estimates, we arrive to the same RV residual rms after correction for activity, but before correction, SN mean RV shows the largest RV rms.

>>>>

When looking at the statistical significance of the different parameters used for correcting activity in Table~\ref{table:alphacent.test}, we see that the intercept is not significant for any of the models, and BIS SPAN (coefficient $\beta_2$) does not statistically significantly help in explaining stellar activity when using the parameters derived from the Normal density fit. 
However all the other parameters in the Normal and SN cases are statistically significant for modeling stellar activity. 
By analyzing the values of the coefficient of determination, $R^2$, we see that the model for the SN mean RV is able to capture the highest percentage of variability in the estimated RV. 
This is not a surprising result since for the three different RV estimates, we arrive to the same RV residual rms after correction for activity, but before correction, SN mean RV shows the largest RV rms (see Fig~\ref{fig:alphacent:correctionRV}).
